### 2014-10-22 thesis/method/classification.tex
Misc fixes to equations
Support vector machines!

For a class variable with two possible values that occur with
probability $p$ and $1-p$ respectively, and a feature vector
$(F_1,F_2,\ldots,F_n)$, the logistic regression model is:
\begin{align*}
\mathrm{logit}(p) &= \mathrm{log} \left(\dfrac{p}{1-p}\right) \\
  &= \beta_0 + \beta_1F_1 + \beta_2F_2 + \ldots + \beta_nF_n
\end{align*}
For LOS classification, this can be rearranged to:
\begin{align*}
p &= \mathbb{P}(Class=\mathrm{LOS }\leq2\mathrm{ days}|F_1,F_2,\ldots,F_n) \\
  &= \dfrac{e^{\beta_0 + \sum^n_{i=1}\beta_i F_i}}{1 + e^{\beta_0 + \sum^n_{i=1}\beta_i F_i}}
\end{align*}

@@

\section{Support Vector Machine (SVM)}

>>>>

For a class variable with two possible values that occur with
probability $p$ and $1-p$ respectively, and a feature vector
$(F_1,F_2,\ldots,F_n)$, the logistic regression model is:
\begin{equation*}
\begin{aligned}
\mathrm{logit}(p) &= \mathrm{log} \left(\dfrac{p}{1-p}\right) \\
  &= \beta_0 + \beta_1F_1 + \beta_2F_2 + \ldots + \beta_nF_n
\end{aligned}
\end{equation*}
For LOS classification, this can be rearranged to:
\begin{equation*}
\begin{aligned}
p &= \mathbb{P}(Class=\mathrm{LOS }\leq2\mathrm{ days}|F_1,F_2,\ldots,F_n) \\
  &= \dfrac{e^{\beta_0 + \sum^n_{i=1}\beta_i F_i}}{1 + e^{\beta_0 + \sum^n_{i=1}\beta_i F_i}}
\end{aligned}
\end{equation*}

@@

\section{Support Vector Machine (SVM)}
Support vector machines (SVMs) are an example of a supervised learning algorithm
capable of classifying training examples into two classes. They are one of the
best algorithms in terms of predictive accuracy \cite{Bellazzi2008}. Despite
this, they have not been widely applied to predicting the LOS, which gives us
an opportunity to evaluate their performance in our LOS classification problem.

Given a set of $n$-feature vectors, we can represent each vector as a point in
$n$-dimensional space, where each feature is a dimension. The SVM will try to
find a \textit{hyperplane} that separates the two classes. Usually there are
many such hyperplanes; the distinguishing aspect of an SVM is that it will
find the hyperplane that maximises the distance between the two nearest points
in each class. This distance is called the \textit{margin}, and the intuition
is that maximising it will give us the greatest possible separation between the
classes -- the classifier comes no closer to either class than it needs to.
This gives the SVM the best generalising ability to classify new examples.

Figure \ref{fig:svm} shows an example of a two-dimensional feature space, with
two classes of points (black and white). We can see the hyperplane, in this
case a line since we are only in two dimensions, separating the two classes
with as much margin as possible. In
this case, the points are linearly separable: all white points lie on one side
of the hyperplane, and all black points lie on the other. In practice, this is
not common, and often data cannot be separated cleanly by a hyperplane.
Note that the points closest to the margin are those that are most likely to be
ambiguous when the data cannot be cleanly separated. The SVM will progressively
remove more and more of these ambiguous points from consideration when it
cannot find a hyperplane until it finds a suitable one.

\begin{figure}[h]
\label{fig:svm}
\caption{}
\centering
%\includegraphics[scale=0.95]{images/a2-nn}
\end{figure}

Instead of removing points from consideration by the SVM, we can also specify
a \textit{kernel function}, which transforms the original feature space into
some other non-linear space. Commonly, polynomial functions of degree 2 or
greater are used, and theoretically they can approximate non-linear boundaries
between classes to any arbitrary accuracy. However, this is usually not
practically possible with data sets containing even a modest number of features
(around 10), due to the computational complexity of estimating a large number
of coefficients that are introduced by the transformation.

SVMs can be specified mathematically as a type of optimisation problem known
as \textit{constrained quadratic optimisation}. Given $m$ training vectors
$\mathbf{x_i} \in \mathbb{R}^n, i=1,\ldots,m$ and their labels
$y_i \in \{-1,+1\}, i=1,\ldots,m$, the optimisation problem can be written as:
\begin{equation}
\label{eqn:svm1}
\begin{aligned}
& \underset{\mathbf{w},b}{\mathrm{minimise}}
  && ||\mathbf{w}|| + C\sum_{i=1,\ldots,m} s_i \\
& \text{subject to}
  && y_i(\mathbf{w}^T\phi(\mathbf{x_i})+b) \geq 1 \\
& && s_i \geq 0, i = 1,\ldots,m
\end{aligned}
\end{equation}
where $\phi(\mathbf{x})$ is the kernel function, and
$\mathbf{w}\cdot\mathbf{x_i} + b = 0$ is the hyperplane that the SVM finds.
The $s_i$'s allow the SVM to ignore some examples if it cannot find a suitable
hyperplane, and $C$ (sometimes called the SVM's complexity constant) is a
constant specified by the user that controls how much we want to balance
finding the best possible margin with allowing misclassified examples.
Note that for a linear kernel, $\phi(\mathbf{x}) = \mathbf{x}$. Training the
SVM involves solving this optimisation problem and obtaining values for
$\mathbf{w}$ and $b$.

To classify an instance $\mathbf{x_{new}}$, we simply find the sign of
$\mathbf{w}\cdot\mathbf{x_{new}}+b$. This will tell us which one of the
two classes the new example belongs to.
